---
title: "CEACT Package"
output: github_document
---


# CEACT: Cost-Effectiveness Analysis for Clinical Trials

## Overview

**CEACT** *(Cost-Effectiveness Analysis for Clinical Trials)* is a tool designed to produce a cost-effectiveness analysis of two interventions, specifically comparing treatment and control groups in clinical trials. This package aims to assist researchers and analysts in making informed decisions based on the cost-effectiveness of different health interventions.

**CEACT** provides a complete suite of functions for computing and visualizing:
- Incremental Cost-Effectiveness Ratio (ICER),
- Cost-effectiveness planes,
- Cost-effectiveness acceptability curves (CEAC),
- Net monetary benefit (NMB) metrics.

---

## Installation

```{r}
# install.packages("devtools")
devtools::install_github("ielbadisy/CEACT")
```

---

## Key Features

- `cea()`: Estimate the ICER and provide summary statistics.
- `boot_icer()`: Perform non-parametric bootstrapping of ICERs.
- `plot_ceplane()`: Plot the cost-effectiveness plane.
- `plot_ceac()`: Plot the cost-effectiveness acceptability curve.
- `compute_nmb_ceac()`: Compute net monetary benefits (NMB) and CEAC tables.

---

## Example Usage

```{r}
# Load CEACT package
library(CEACT)

# Simulate example data from a clinical trial
set.seed(123)
control <- data.frame(
  cost = rnorm(200, 500, 100),
  effect = rnorm(200, 0.4, 0.05),
  group = "control"
)

treatment <- data.frame(
  cost = rnorm(200, 550, 100),
  effect = rnorm(200, 0.3, 0.06),
  group = "treatment"
)

data <- rbind(control, treatment)
```

```{r}
# Run cost-effectiveness analysis
res_cea <- cea(cost + effect ~ group, data = data, ref = "control")
res_cea
```

```{r}
# Bootstrap ICER distribution
res_boot <- boot_icer(cost + effect ~ group, data = data, ref = "control", R = 300)
res_boot$summary
```

```{r}
# Plot Cost-Effectiveness Plane
plot_ceplane(res_boot, k = 1000)
```

# Plot Cost-Effectiveness Acceptability Curve
plot_ceac(res_boot, wtp_range = seq(0, 2000, 100))

# Compute Net Monetary Benefit and CEAC Table
nmb_table <- compute_nmb_ceac(
  data = data.frame(c = res_boot$boot_dist[, 1], e = res_boot$boot_dist[, 2]),
  wtp_range = seq(0, 2000, 100)
)
print(nmb_table)
```

---

## Documentation

You can access documentation for each function using:

```r
?cea
?boot_icer
?plot_ceplane
?plot_ceac
?compute_nmb_ceac
```

---

## Feedback & contributions

We welcome feedback and contributions.  
Submit suggestions, feature requests, or report issues via [GitHub Issues](https://github.com/ielbadisy/CEACT/issues).

---
