---
title: "CEACT Package"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", fig.width = 7, fig.height = 4.5)
```

## Overview

**CEACT** *(Cost-Effectiveness Analysis for Clinical Trials)* is an R package for two-arm trial-based economic evaluation. It implements a formula-based workflow for:

- observed incremental cost, incremental effect, and ICER summaries;

- stratified non-parametric bootstrap uncertainty;
- incremental net monetary benefit (INMB);

- cost-effectiveness acceptability curves (CEACs);

- cost-effectiveness planes;

- one-way deterministic sensitivity analysis.

CEACT is intended for individual-level clinical-trial datasets with one cost
variable, one effect variable, and a two-level treatment group.

## Installation

```{r eval=FALSE}
# install.packages("devtools")
devtools::install_github("ielbadisy/CEACT")
```

```{r}
library(CEACT)
```

## Simulate Trial Data

```{r}
trial <- simulate_ce_trial(n = 200, seed = 123)
head(trial)
```

## Observed Cost-Effectiveness Summary

```{r}
res_cea <- cea(cost + effect ~ group, data = trial, ref = "control")
summary(res_cea)
```

## Bootstrap Uncertainty

```{r}
set.seed(42)
res_boot <- boot_icer(cost + effect ~ group, data = trial, ref = "control",
                      R = 500, ci.type = "perc")
summary(res_boot)
```

## Cost-Effectiveness Plane

```{r}
plot_ceplane(res_boot, k = 20000)
```

## Net Monetary Benefit and CEAC

```{r}
ceac_table <- compute_nmb_ceac(res_boot, wtp_range = seq(0, 50000, 5000))
head(ceac_table)
plot_ceac(ceac_table)
```

## Deterministic Sensitivity Analysis

```{r}
dsa_result <- dsa_icer(cost + effect ~ group, data = trial,
                       param = "effect",
                       range = seq(0.74, 0.82, 0.02),
                       ref = "control",
                       metric = "INMB",
                       k = 20000)
dsa_result
plot_dsa(dsa_result, metric = "INMB")
```

## Trial-Based CEA Dataset

CEACT also includes `trial_cea`, a 500-patient example dataset with treatment, total cost, and QALY outcomes used in teaching material for trial-based economic evaluation.

```{r}
data("trial_cea")
real_res <- cea(cost + qaly ~ group, data = trial_cea, ref = "control")
summary(real_res)
```

## Package Quality

- Unit tests are implemented with **testthat**.

- Function documentation is generated with **roxygen2**.

- A PDF vignette is available in `vignettes/`.

- The package source builds and checks successfully with `R CMD check`.
