---
title: "CEACT Package"
output: github_document
---

# CEACT: Cost-Effectiveness Analysis for Clinical Trials

## Overview

**CEACT** *(Cost-Effectiveness Analysis for Clinical Trials)* is an R package designed to facilitate the economic evaluation of healthcare interventions in randomized trials. It offers a suite of functions for estimating and visualizing core cost-effectiveness metrics, including:

- Incremental Cost-Effectiveness Ratios (ICER),
- Cost-effectiveness planes,
- Cost-effectiveness acceptability curves (CEAC),
- Net monetary benefit (NMB) metrics.

CEACT is built using a formula-friendly, tidyverse-inspired interface to streamline analysis workflows.

---

## Installation

```{r}
# Install from GitHub using devtools
# install.packages("devtools")
#devtools::install_github("ielbadisy/CEACT")
library(CEACT)
```

---

## Key Features

- `cea()`: Estimate ICER and generate a descriptive cost-effectiveness summary.
- `boot_icer()`: Perform bootstrap-based uncertainty analysis for ICER.
- `plot_ceplane()`: Visualize the cost-effectiveness plane with optional quadrant breakdown.
- `plot_ceac()`: Plot the cost-effectiveness acceptability curve.
- `compute_nmb_ceac()`: Compute expected NMB and probability of cost-effectiveness across WTP values.

---

## Example Usage

### Simulate Trial Data

```{r}
set.seed(123)

control <- data.frame(
  cost = rnorm(200, 500, 100),
  effect = rnorm(200, 0.4, 0.05),
  group = "control"
)

treatment <- data.frame(
  cost = rnorm(200, 550, 100),
  effect = rnorm(200, 0.3, 0.06),
  group = "treatment"
)

df <- rbind(control, treatment)
```

### Run Cost-Effectiveness Analysis

```{r}
res_cea <- CEACT::cea(cost + effect ~ group, data = df, ref = "control")
summary(res_cea)
```

### Bootstrap the ICER

```{r}
res_boot <- CEACT::boot_icer(cost + effect ~ group, data = df, ref = "control", R = 300)
summary(res_boot)
```

### Visualize the Cost-Effectiveness Plane

```{r}
CEACT::plot_ceplane(res_boot, k = 1000)
```

### Plot the CEAC

```{r}
CEACT::plot_ceac(res_boot, wtp_range = seq(0, 20000, 1000))
```

### Compute NMB and CEAC Table

```{r}
nmb_table <- CEACT::compute_nmb_ceac(cost + effect ~ 1, data = df, wtp_range = seq(0, 20000, 1000))
head(nmb_table)
```

---

## Feedback & Contributions

We welcome feedback, issues, and pull requests.  
Contribute via the [GitHub Issues page](https://github.com/ielbadisy/CEACT/issues).

---

## TODO

- [x] Formula-based interface across all functions
- [x] Optional quadrant labels in CE plane
- [x] Improved p-value formatting
- [x] Complete function-level documentation using **roxygen2**
- [x] Fix warnings and notes
- [ ] Add unit tests using **testthat**
- [ ] Create a PDF vignette
- [ ] Write a comprehensive tutorial or use-case article
- [ ] Submit to **CRAN**

---


